--
title: 'Exploration 13: Workflow'
author: 'Kristin, Josh, Miles, Ying'
date: '`r format(Sys.Date(), "%B %d, %Y")`'
fontsize: 10pt
geometry: margin=1in
mainfont: "Crimson Text"
output:
  pdf_document:
    latex_engine: xelatex
    fig_caption: yes
    fig_height: 4
    fig_width: 4
---



```{r include=FALSE, cache=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).
# knitr settings to control how R chunks work.

## To make the html file do
## render("exploration4.Rmd",output_format=html_document(fig_retina=FALSE))
## To make the pdf file do
## render("exploration4.Rmd",output_format=pdf_document())

require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  echo=TRUE,
  results='markup',
  strip.white=TRUE,
  fig.path='figs/fig',
  cache=FALSE,
  highlight=TRUE,
  width.cutoff=132,
  size='footnotesize',
  out.width='.9\\textwidth',
  fig.retina=FALSE,
  message=FALSE,
  comment=NA)

if(!file.exists('figs')) dir.create('figs')

options(SweaveHooks=list(fig=function(){
			   par(mar=c(3.5, 3, 1.1, 0),
			       pty="s",
			       mgp=c(1.5,0.5,0),
			       oma=c(0,0,0,0))},
			 echo=function(){options(continue=" ") ##Don't show "+" prompts,
			 options(prompt=" ")
			 }),
	digits=4,
	scipen=8,
	width=132
	)
options(error=function(){options(prompt="> ",continue="+ ");NULL})
```


```{r}
library(readstata13)
## code book http://www.jakebowers.org/PS531/anes_timeseries_2016_userguidecodebook.pdf
anes16 <- read.dta13("http://jakebowers.org/PS531/anes_timeseries_2016.dta")
## V162034a Numeric POST: For whom did R vote for President
## YL:
# -9. Refused
# -8. Don't know (FTF only)
# -7. No Post, deleted due to insufficient partial
# -6. Unit nonresponse, no Post-Election interview
# 1. Hillary Clinton
# 2. Donald Trump
# 3. Gary Johnson
# 4. Jill Steiin
# 5. Other candidate SPECIFY
# 7. Other specify given as: none
# 9. Other specify given as: RF
# YL ends
table(anes16$V162034a,exclude=c())
### Some recoding (but not all) in here
source("Data/nes16setup.R") # YL: is this in Jake's computer?
```

```{r}
library(rstanarm)
```

**The question:** Which predicts Trump vote more strongly --- socioeconomic status or beliefs about immigration?

# YL
To solve this question, we first need to find the variables that are related to socioeconomic status and immigration in the dataset. The following is what I found. The first two are about immigration. Then follows something that might indicate socioeconomic status. 
1. V162157 Numeric POST: What should immigration levels be. Do you think the number of immigrants from foreign countries who are permitted to come to the United States to live should be [1 increased a lot, 2 increased a little, 3 left the same as it is now, 4 decreased a little, or 5 decreaseda lot; -9 Refused, -8 Don't know, -7 No post data, deleted due to incomplete IW; -6 No post-election interview]?
2. V162158 Numeric POST: How likely immigration will take away jobs. How likely is it that recent immigration levels will take jobs away from people already here -- [1 extremely likely, 2 very likely, 3 somewhat likely, or 4 not at all likely]

V161270 PRE: Highest level of Education

V161304 PRE: Think of self as belonging to class
V161305a PRE: Social Class: working or middle
V161305b PRE: Social Class: had to choose working middle
V161306 PRE: Social class: average or upper working middle class 
V161307 PRE: Social class (2-question version)
V161307a PRE: EGSS social class if middle class
V161308x PRE: SUMMARY - R self-identified social class
V162132 POST: R social class

V161361x PRE FTF CASI/WEB: Pre income summary

Question: 1. we need to choose which variables we are using as independent variables
2. Pre or Post?
3. Should we add some control variables? If so, what are they?
Are you guys more familiar than me with this dataset? I'm definitely not reliable when it comes to politics studies!
# YL ends

**The overall task:** Create a reproducible workflow and practice writing about Bayesian approaches to data analysis.

Details: (YL rearranged the order of the following instructions)
Step 1
 - Make a new github repository for your group to use for collaboration: Decide if you want to have each group member fork or just use branches for pull requests within the group.
YL: Check! We are not forking. We even don't use branches, because as a small group, face-to-face meetings enable us to solve problems immediately via discussion.

Step2
- The text should should be written in LaTeX or R+markdown and should involve a bibliography that is automatically generated using either bibtex or biblatex. The text should be about 1 page and involve one figure and/or one table in addition to an interpretation and explanation of the meaning of the results. (Imagine it as the results section of a paper, but shorter.)
YL: We are doing this right now.

Step3
 - Each task requires its own file: you will want a file for data cleaning, a file for data analysis (say, fitting linear models), a file per figure or table, a file for text.
YL: I'm a bit confused here. So we should divide the whole project into different parts and store them as independent files in Github repo?

Step4
  - Use the `rstanarm` package to produce posterior distributions of model quantities (like coefficients and/or predictions) address this question.

Step5
 - Someone who wanted to reproduce the work they should be able to do so automatically --- without opening and running each file --- and they should be able to do so on their own computer. What system will you use for this?
    - You may use the old Make system (https://www.google.com/search?q=makefiles+and+r&oq=makefiles+and+r)
    - Or R oriented approaches like `drake` (https://github.com/ropensci/drake) or `remake` (https://github.com/richfitz/remake) or `snakemake` (https://snakemake.readthedocs.io/en/stable/)
    - Or something else.



# References