--
title: 'Exploration 13: Workflow'
author: 'Jake Bowers'
date: '`r format(Sys.Date(), "%B %d, %Y")`'
fontsize: 10pt
geometry: margin=1in
mainfont: "Crimson Text"
output:
  pdf_document:
    latex_engine: xelatex
    fig_caption: yes
    fig_height: 4
    fig_width: 4
---



```{r include=FALSE, cache=FALSE}
# Some customization.  You can alter or delete as desired (if you know what you are doing).
# knitr settings to control how R chunks work.

## To make the html file do
## render("exploration4.Rmd",output_format=html_document(fig_retina=FALSE))
## To make the pdf file do
## render("exploration4.Rmd",output_format=pdf_document())

require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  echo=TRUE,
  results='markup',
  strip.white=TRUE,
  fig.path='figs/fig',
  cache=FALSE,
  highlight=TRUE,
  width.cutoff=132,
  size='footnotesize',
  out.width='.9\\textwidth',
  fig.retina=FALSE,
  message=FALSE,
  comment=NA)

if(!file.exists('figs')) dir.create('figs')

options(SweaveHooks=list(fig=function(){
			   par(mar=c(3.5, 3, 1.1, 0),
			       pty="s",
			       mgp=c(1.5,0.5,0),
			       oma=c(0,0,0,0))},
			 echo=function(){options(continue=" ") ##Don't show "+" prompts,
			 options(prompt=" ")
			 }),
	digits=4,
	scipen=8,
	width=132
	)
options(error=function(){options(prompt="> ",continue="+ ");NULL})
```


```{r}
library(readstata13)
## code book http://www.jakebowers.org/PS531/anes_timeseries_2016_userguidecodebook.pdf
anes16 <- read.dta13("http://jakebowers.org/PS531/anes_timeseries_2016.dta")
## V162034a Numeric POST: For whom did R vote for President
table(anes16$V162034a,exclude=c())
### Some recoding (but not all) in here
source("Data/nes16setup.R") 
```

```{r}
library(rstanarm)
```


**The question:** Which predicts Trump vote more strongly --- socioeconomic status or beliefs about immigration?

**The overall task:** Create a reproducible workflow and practice writing about Bayesian approaches to data analysis.

Details:
 - Use the `rstanarm` package to produce posterior distributions of model quantities (like coefficients and/or predictions) address this question.
 - Make a new github repository for your group to use for collaboration: Decide if you want to have each group member fork or just use branches for pull requests within the group.
 - Each task requires its own file: you will want a file for data cleaning, a file for data analysis (say, fitting linear models), a file per figure or table, a file for text.
 - The text should should be written in LaTeX or R+markdown and should involve a bibliography that is automatically generated using either bibtex or biblatex. The text should be about 1 page and involve one figure and/or one table in addition to an interpretation and explanation of the meaning of the results. (Imagine it as the results section of a paper, but shorter.)
 - Someone who wanted to reproduce the work they should be able to do so automatically --- without opening and running each file --- and they should be able to do so on their own computer. What system will you use for this?
    - You may use the old Make system (https://www.google.com/search?q=makefiles+and+r&oq=makefiles+and+r)
    - Or R oriented approaches like `drake` (https://github.com/ropensci/drake) or `remake` (https://github.com/richfitz/remake) or `snakemake` (https://snakemake.readthedocs.io/en/stable/)
    - Or something else.



# References